### 2017-10-17 sheets/basis-1/sheet-basis-1.tex
Fixed compilation bugs on sheet 1

\begin{document}

% Use Basis x or Talk x, where x is the number of the session
\uebunghead{Basis 1}{What is a Category?}

@@

@@

@@

\begin{definition}{Pos} The objects of  \textbf{Pos} are partially ordered sets
(recall that a poset is a set $A$ equipped with a reflexive, transitive and antisymmetric binary relation $\leq^A$). The morphisms $m \from A \to B $ are monotone functions: $a \leq^A a' \implies m(a) \leq^A m(a')$
\end{definition}

@@

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

>>>>

\begin{document}
% Use Basis x or Talk x, where x is the number of the session
\uebunghead{Basis 1}{What is a Category?}

@@

%\section{Diagrams}
%
%\begin{hint}
%  This is how you can draw diagrams:
%  \[
%    \begin{tikzcd}
%                                    & A \arrow{dr}{g}    & \\
%      B \arrow{ur}{f} \arrow{rr}{h} &                    & C
%    \end{tikzcd}
%  \]
%\end{hint}

@@

\begin{definition}{Pos} The objects of  \textbf{Pos} are partially ordered sets 
(recall that a poset is a set $A$ equipped with a reflexive, transitive and antisymmetric binary relation $\leq^A_\cdot $ ) 
An arrow $ m \from A \to B $ function that is monotone, i.e. $\forall a, a' \in A$, 
\[a \leq^A_\cdot a' \implies m(a) \leq^A_\cdot m(a')\]
\end{definition}

@@

@@

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
